The Two Dualities of Computation: Negative and Fractional Types

### 2012-02-29 rational.tex
sat

>>>>

The construction presented here is a novel SAT-solver that relies on
{{trace*}} for its solution. It varies from previous classical SAT
solvers in that there is not explicit search operation on the boolean
space. It also varies from previous quantum SAT solvers in that it
does uses a {{trace}} operation to compute a fixpoint which is the
solution following which an isomorphic clone operation allows us to
examine the result.

The construction here is not limited to boolean satisfiability, but
generalises to any constraint satisfaction problem whose search space
can be represented by a recursive type and for which an isomorphic
clone operation can be constructed. That said, we will focus on the
limited case of boolean satisfiability here.

Consider the circuit below that has no observable output -- i.e. for
all inputs it is annihilating. This happens because it constructs a
boolean and its dual, negates one of them and attempts to collapse
them.
\begin{center}
\scalebox{1.5}{
  \includegraphics{diagrams/not_trace.pdf}
}
\end{center}

We leverage the basic idea of the above circuit, to collapse all
values that are not solutions to the specified isomorphic constraint
{{f}}. The operation {{f}} acts on some inputs and its adjoint
reconstructs the inputs from the outputs. While the output of {{f}}
may contain many components, its must contain a boolean indicating if
the input satisfy {{f}}. The special output wire is used to `control'
the negation of a boolean `control wire'. If the inputs do not satisfy
{{f}}, the control wire is negated.

\begin{center}
\scalebox{1.5}{
  \includegraphics{diagrams/sat1.pdf}
}
\end{center}

If this construction is traced using {{trace*}}, all the values that
do not satisfy {{f}} get annihilated because the control wire acts
like the closed-loop `not' in the previous construction.
